---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lightparser

<!-- badges: start -->
[![R-CMD-check](https://github.com/ThinkR-open/lightparser/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ThinkR-open/lightparser/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/ThinkR-open/lightparser/branch/main/graph/badge.svg)](https://app.codecov.io/gh/ThinkR-open/lightparser?branch=main)
<!-- badges: end -->

You need to extract some specific information from your Rmd or Qmd file?
{lightparser} is designed to split your Rmd or Qmd file by sections into a tibble: titles, text, chunks.
It stores them as a tibble, so you can easily manipulate it with dplyr or purrr.
Later, you can rebuild a Rmd or Qmd from the tibble.

This is a light version of {parsermd} that has not been updated for a long time, 
and which is not compatible with the latest versions of C++ compilers.
{lightparser} does not rely on C++ compilation.

## Installation

You can install the development version of lightparser from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ThinkR-open/lightparser")
```

## Documentation

Full documentation website on: https://ThinkR-open.github.io/lightparser

## Example

Split your Rmd or Qmd file into a tibble:

```{r}
library(lightparser)

file <- system.file(
  "dev-template-parsing.Rmd",
  package = "lightparser"
)
tbl_rmd <- split_to_tbl(file)
tbl_rmd
```

Combine the tibble into a Rmd or Qmd file:

```{r}
combine_tbl_to_file(tbl_rmd, tempfile(fileext = ".Rmd"))
```

## Code of Conduct

Please note that the lightparser project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.