---
title: "Development actions history"
output: html_document
editor_options: 
  chunk_output_type: console
---

All commands that you use to use when developing packages...

# First time just after creating the project

- Fill the following chunk to create the DESCRIPTION of your package

```{r description}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "From Rmd and Qmd to Tibble and Back",
    Description = "Split your Rmd or Qmd file by sections into a tibble: titles, text, chunks. Rebuild it from the tibble.",
    `Authors@R` = c(
      person(
        "Sebastien", "Rochette",
        email = "sebastien@thinkr.fr",
        role = c("aut", "cre"),
        comment = c(ORCID = "0000-0002-1565-9313")
      ),
      person(given = "ThinkR", role = "cph")
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("ThinkR")
```

# All-in-one function to deploy publicly on GitHub

Either use this GitHub all-in-one function or choose the steps one-by-one in the following sections.
See `vignette("share-on-a-github-website", package = "fusen")` for more information.

```{r, eval=FALSE}
# _All-in-one share of your package and its documentation on GitHub
fusen::init_share_on_github(organisation = "ThinkR-open")
```


# Start using git

```{r, eval=FALSE}
usethis::use_git()
# Deal with classical files to ignore
usethis::git_vaccinate()
# Use main for primary branch
usethis::git_default_branch_rename()
```

# Set extra sources of documentation

```{r, eval=FALSE}
# Install a first time
remotes::install_local()
# Code of Conduct
usethis::use_code_of_conduct("coc@thinkr.fr")
```

**From now, you will need to "inflate" your package at least once to be able to use the following commands. Let's go to your flat template, and come back here later if/when needed.**


# Package development tools
## Use once

```{r, eval=FALSE}
# Pipe
usethis::use_pipe()

# package-level documentation
usethis::use_package_doc()

# New testthat version
usethis::use_testthat()
```

## Use everytime needed

```{r, eval=FALSE}
# Simulate package installation
pkgload::load_all()

# Generate documentation and deal with dependencies
attachment::att_amend_desc(
  pkg_ignore = c("fusen", "usethis", "callr"),
  extra.suggests = c("callr"),
  update.config = TRUE
)

# Check the package
devtools::check()

# Clean the code
styler::style_pkg()
styler::style_dir("dev/")

# Add a new flat template
fusen::add_flat_template("add")

# Build Readme
devtools::build_readme()
```

## Prepare for CRAN

```{r, eval=FALSE}
# Run examples in interactive mode too
devtools::run_examples()

# Check package as CRAN
rcmdcheck::rcmdcheck(args = c("--no-manual", "--as-cran"))
devtools::check(args = c("--no-manual", "--as-cran"))

# Check content
# remotes::install_github("ThinkR-open/checkhelper")
tags <- checkhelper::find_missing_tags()
View(tags$functions)

# Remettre: Config/testthat/parallel: false dans DESCRIPTION
out <- checkhelper::check_clean_userspace(pkg = ".")
out
checkhelper::check_as_cran()
# Remettre: Config/testthat/parallel: true dans DESCRIPTION

# Check spelling
# usethis::use_spell_check()
spelling::spell_check_package()

# Check URL are correct
# remotes::install_github("r-lib/urlchecker")
urlchecker::url_check()
urlchecker::url_update()

# Upgrade version number
usethis::use_version(which = c("patch", "minor", "major", "dev")[2])

# check on other distributions
# _rhub
devtools::check_rhub()
rhub::platforms()
rhub::check_on_windows(check_args = "--force-multiarch", show_status = FALSE)
rhub::check_on_solaris(show_status = FALSE)
rhub::check(platform = "debian-clang-devel", show_status = FALSE)
rhub::check(platform = "debian-gcc-devel", show_status = FALSE)
rhub::check(platform = "fedora-clang-devel", show_status = FALSE)
rhub::check(platform = "macos-m1-bigsur-release", show_status = FALSE)
rhub::check_for_cran(show_status = FALSE)


rhub::check(platform = "windows-x86_64-devel", show_status = FALSE)

# _win devel
devtools::check_win_devel()
devtools::check_win_release()
# remotes::install_github("r-lib/devtools")
devtools::check_mac_release()

# Update NEWS
# Bump version manually and add list of changes

# Add comments for CRAN
usethis::use_cran_comments(open = rlang::is_interactive())

# Upgrade version number
usethis::use_version(which = c("patch", "minor", "major", "dev")[1])

# Verify you're ready for release, and release
devtools::release()

# Back to dev
usethis::use_version(which = c("patch", "minor", "major", "dev")[4])
```

